\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{datetime}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Yiğit Efe Avcı}} \hspace{2pt} {\LARGE{Full-Stack Developer}}\\[10pt]
        \href{mailto:yigit433.devs@gmail.com}{yigit433.devs@gmail.com} \textbullet\
        \href{https://github.com/yigit433}{github.com/yigit433} \textbullet\
        \href{https://linkedin.com/in/yigitefeavci}{linkedin.com/in/yigitefeavci} \textbullet\
        \href{https://yigit433.vercel.app}{yigit433.vercel.app}
    \end{minipage}
\end{center}
\section{About Me}
I am a statistics undergraduate with a strong interest in data science, software development, and statistical modeling. I specialize in transforming data into actionable insights using tools like Python, R, and SPSS. My technical focus extends to full-stack development, where I utilize technologies such as React, Next.js, Go, and PostgreSQL to build scalable, efficient, and user-centric web applications.
\section{Experience}
\textbf{\href{https://codeshare.me}{Code Share}} \hfill London, United Kingdom\\
\textit{Managing Partner (Self-employed)} \hfill August 2020 -- May 2025\\
\textit{Software Developer (Freelance, Remote)} \hfill June 2019 -- June 2023\\[6pt]
\textbf{WiFiCeps} \hfill Türkiye\\
\textit{Backend Developer (Project-based)} \hfill January 2023 -- February 2023
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Developed a custom media server for the WiFiCeps educational platform.
    \item Designed a system that monitored videos uploaded to Google Drive, detected updates, and automatically synchronized them with the platform's existing versions.
    \item Implemented an automated process that removed videos from the media server when they were deleted from Google Drive.
    \item Built a Python-based automation framework and an FFmpeg-powered video processing algorithm.
    \item Optimized video size and quality, reducing files to approximately \textasciitilde50MB through automated processing.
    \item Significantly reduced playback issues and improved overall streaming performance.
\end{itemize}
\textbf{Konda Research and Consultancy} \hfill Türkiye\\
\textit{Field Researcher (Surveyor)} \hfill Month Year -- Month Year
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Conducted fieldwork for nationwide surveys, including face-to-face interviews and data collection.
    \item Ensured accurate and reliable input for research projects by following methodological standards and engaging directly with participants.
\end{itemize}
\section{Projects}
\textbf{\href{https://pickin.co}{Pickin} — Real-time giveaway platform} \hfill Next.js, TypeScript, PostgreSQL\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Real-time participant and state updates via Server-Sent Events backed by Redis Pub/Sub.
    \item Scheduled giveaway start/end and automatic winner selection via NATS JetStream job queue.
    \item OAuth-gated participation rules (YouTube subscribe/like, Twitch follow) using Better Auth.
    \item RBAC system (4 roles, 15 permissions), i18n (TR/EN), QR sharing, OBS broadcast view, CSV export.
    \item Stack: Next.js 16 (App Router, Turbopack), Drizzle ORM, Tailwind CSS v4, Framer Motion, TipTap, Docker.
\end{itemize}
\textbf{\href{https://deckplane.com}{Deckplane} — Distributed Docker management platform} \hfill Bun, Hono, TypeScript, PostgreSQL\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Designed a control-plane / host-agent architecture: agents on each Docker host communicate with a central API via WebSocket and REST.
    \item Manage containers, images, networks and volumes across multiple servers from a single API with an async command queue.
    \item WebSocket-based interactive container terminal with session recording, plus real-time log and CPU/memory stat streaming.
    \item Deployment automation from GitHub repos or docker-compose archives, with OAuth-based GitHub integration (branches, secrets, webhooks).
    \item RBAC (4 roles), multi-tenancy, immutable audit logging, token-bucket rate limiting, auto-generated OpenAPI 3.0 + Swagger UI.
    \item Stack: Bun, Hono, Drizzle ORM, JWT (jose) + Argon2, Zod, Pino, AES-256-GCM, Traefik (HTTPS + WebSocket).
\end{itemize}
\textbf{\href{https://github.com/yigit433/kommando}{kommando} — CLI toolkit for Go} \hfill Go\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Lightweight library for building command-line tools with subcommands and flag parsing.
    \item Focused on ergonomic API design and zero external dependencies.
\end{itemize}
\textbf{\href{https://github.com/yigit433/helper-tui}{helper-tui} — Terminal UI utility} \hfill Rust\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Cross-platform TUI that streamlines common developer workflows from the terminal.
    \item Built in Rust with an emphasis on responsiveness and minimal binary size.
\end{itemize}
\textbf{\href{https://github.com/yigit433/feather-stream}{feather-stream} — Google Drive media player} \hfill Tauri, React, TypeScript\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Desktop application for streaming media files stored on Google Drive.
    \item Built end-to-end with Tauri (Rust core) and a React/TypeScript frontend.
\end{itemize}
\textbf{\href{https://github.com/yigit433/jsonparser}{jsonparser} — JSON parser written in C} \hfill C\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item From-scratch JSON document parser and processor implemented in C.
    \item Hand-written tokenizer and recursive-descent parser; no external dependencies.
\end{itemize}
\section{Skills}
\textbf{Languages:} Python, R, TypeScript, JavaScript, GoLang, Rust, Dart \\
\textbf{Data \& ML:} Pandas, Polars, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch, SPSS \\
\textbf{Backend:} Bun, Node.js, Express.js, REST APIs \\
\textbf{Frontend:} React, Next.js, Tailwind CSS, Framer Motion \\
\textbf{Mobile / Cross-Platform:} Flutter, React Native, Tauri \\
\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Supabase \\
\textbf{Tools:} Git, Docker, Drizzle ORM, Postman
\section{Education}
\textbf{Istanbul Commerce University} \hfill Istanbul, Türkiye\\
\textit{B.Sc. in Statistics} \hfill 2023 -- 2027\\
\end{document}
