\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{datetime}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Yiğit Efe Avcı}} \hspace{2pt} {\LARGE{Statistics \& Data Science}}\\[10pt]
        \href{mailto:yigit433.devs@gmail.com}{yigit433.devs@gmail.com} \textbullet\
        \href{https://github.com/yigit433}{github.com/yigit433} \textbullet\
        \href{https://linkedin.com/in/yigitefeavci}{linkedin.com/in/yigitefeavci} \textbullet\
        \href{https://yigit433.vercel.app}{yigit433.vercel.app}
    \end{minipage}
\end{center}
\section{Education}
\textbf{Istanbul Commerce University} \hfill Istanbul, Türkiye\\
\textit{B.Sc. in Statistics} \hfill 2023 -- 2027\\
\section{Profile}
Statistics undergraduate with a strong interest in data science, statistical modeling, and survey research. Hands-on experience with Python, R, and SPSS, alongside modern data libraries (Pandas, Polars, Scikit-learn). Combine nationwide fieldwork experience with software engineering skills used to build data collection, automation, and enrichment tools.
\section{Experience}
\textbf{Konda Research and Consultancy} \hfill Türkiye\\
\textit{Field Researcher (Surveyor)} \hfill Month Year -- Month Year
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Conducted fieldwork for nationwide surveys, including face-to-face interviews and data collection.
    \item Ensured accurate and reliable input for research projects by following methodological standards and engaging directly with participants.
\end{itemize}
\textbf{WiFiCeps} \hfill Türkiye\\
\textit{Backend Developer (Project-based)} \hfill January 2023 -- February 2023
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built a Python-based automation framework with an FFmpeg-powered video processing pipeline.
    \item Designed a system that monitored Google Drive uploads, detected updates, and synchronized them with the platform automatically.
    \item Optimized video size and quality through automated processing, reducing files to approximately \textasciitilde50MB.
\end{itemize}
\textbf{\href{https://codeshare.me}{Code Share}} \hfill London, United Kingdom\\
\textit{Managing Partner (Self-employed)} \hfill August 2020 -- May 2025\\
\textit{Software Developer (Freelance, Remote)} \hfill June 2019 -- June 2023\\
\section{Projects}
\textbf{\href{https://pickin.co}{Pickin} — Real-time giveaway platform} \hfill Next.js, TypeScript, PostgreSQL\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Real-time participant and state updates via Server-Sent Events backed by Redis Pub/Sub.
    \item Scheduled job processing via NATS JetStream and OAuth-gated participation rules.
\end{itemize}
\textbf{\href{https://deckplane.com}{Deckplane} — Distributed Docker management platform} \hfill Bun, Hono, TypeScript, PostgreSQL\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Control-plane / host-agent architecture; agents communicate with a central API via WebSocket and REST.
    \item Deployment automation from GitHub repos with RBAC, audit logging, and auto-generated OpenAPI 3.0 docs.
\end{itemize}
\section{Skills}
\textbf{Data \& Statistics:} Python, R, SPSS, Pandas, Polars, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch \\
\textbf{Languages:} Python, R, TypeScript, JavaScript, GoLang, Rust, Dart \\
\textbf{Engineering:} Node.js, Bun, Next.js, React, PostgreSQL, MongoDB, Docker \\
\textbf{Tools:} Jupyter, Git, Drizzle ORM, Postman
\end{document}
